### 2017-06-15 paper.tex
language and citation for git, resolving #7

Tools can help,
especially if they allow proposed changes to be viewed and discussed
prior to their incorporation/merger into the lessons
(in open source software development this is known as ``pre-merge review'').
Providing a gentle on-ramp for new contributors is essential,
but some tools come with a considerable up-front learning curve.
GitHub with pull requests is ideal for pre-merge review, for instance,
but it requires contributors to know how to use Git,
which is a famously user-hostile tool.
Allowing people to edit a Google Doc or Wiki-based editing does not offer pre-merge review,
but the low barrier to entry can help get conversations started.

@@

>>>>

Tools can help,
especially if they allow proposed changes to be viewed and discussed
prior to their incorporation/merger into the lessons
(in open source software development this is known as ``pre-merge review'').
Providing a gentle on-ramp for new contributors is essential,
but some tools come with a considerable up-front learning curve.
Housing lessons on GitHub with changes suggested via pull requests is 
ideal for pre-merge review, for instance,
but it requires contributors to know how to use Git,
which has a notoriously steep learning curve \cite{git-survey}.
Allowing people to edit a Google Doc or Wiki-based editing does not offer pre-merge review,
but the low barrier to entry can help get conversations started.

@@

\bibitem{git-survey}
GitLab
\newblock Global Developer Survey.
\newblock http://get.gitlab.com/global-developer-survey/; 2016.
